Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-09-11 awipev-CO2.Rmd
text updated in SNAPO part according to flags changement from 3 to 2 for 3 dates

>>>>

Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have been flaged "3" by the SNAPO. After a close look, these samples are not differents from their duplicates. Then we put the flag to "2" (good result).

For TA and CT, samples's flags that have been changed from 3 to 2 are: 2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268 and 2116).
